\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{titlesec}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

\setlength{\parindent}{0pt}
\pagestyle{plain}

\begin{document}

\begin{center}
{\LARGE \textbf{Paul S. Willen}}\\[6pt]
{\large Senior Economist and Policy Advisor}\\
Research Department, Federal Reserve Bank of Boston\\[6pt]
Phone: (617) 620-3696 \quad Email: \href{mailto:paul.willen@bos.frb.org}{paul.willen@bos.frb.org}
\end{center}

\section*{Positions}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Federal Reserve Bank of Boston}, Senior Economist and Policy Advisor, 2007--present
\item \textbf{Harvard University}, Visiting Lecturer, Department of Economics, 2022, 2016--2019, 2014
\item \textbf{MIT}, Visiting Associate Professor of Economics, 2013--2014, 2006--2008
\item \textbf{National Bureau of Economic Research}, Faculty Research Fellow, 2004--present
\item \textbf{University of Chicago}, Graduate School of Business, Assistant Professor, 2000--2004
\item \textbf{Princeton University}, Department of Economics, Assistant Professor, 1997--2000
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Ph.D., M.Phil., M.A.} Economics, Yale University (1997, 1995, 1994)\\
Committee: John Geanakoplos, Robert Shiller, Bill Brainard
\item \textbf{B.A.} Economics, Williams College (1990)
\end{itemize}

\section*{Working Papers}
\begin{enumerate}[leftmargin=*, nosep]
\item ``Is there a Puzzle in Underwater Mortgage Default?'' (with David Hao Zhang, Lara Loewenstein, and Yuxi Yao) -- R\&R, \textit{Journal of Financial Economics}
\item ``Testing for Discrimination in Menus'' (with David Hao Zhang) -- R\&R, \textit{American Economic Review}
\item ``House Prices and Rents in the 21st Century'' (with Lara Loewenstein) -- 2023
\end{enumerate}

\section*{Journal Publications}
\begin{enumerate}[leftmargin=*, nosep]
\item ``How Resilient Is Mortgage Credit Supply? Evidence from the COVID-19 Pandemic'' (with Andreas Fuster, Aurel Hizmo, Lauren Lambie-Hanson, and James Vickery). Forthcoming, \textit{Journal of Finance}.
\item ``Technological Innovation in Mortgage Underwriting and the Growth in Credit, 1985--2015'' (with Chris Foote and Lara Loewenstein). Forthcoming, \textit{Journal of Urban Economics}.
\item ``The Time-Varying Price of Financial Intermediation in the Mortgage Market'' (with Andreas Fuster and Stephanie Lo). 2024. \textit{Journal of Finance} 79(4): 2553--2602.
\item ``Mortgage Prepayment, Race, and Monetary Policy'' (with Kristopher Gerardi and David Hao Zhang). 2023. \textit{Journal of Financial Economics} 147(3): 498--524.
\item ``Cross-Sectional Patterns of Mortgage Debt during the Housing Boom: Evidence and Implications'' (with Chris Foote and Lara Loewenstein). 2021. \textit{Review of Economic Studies} 88(1): 229--259.
\item ``Can't Pay or Won't Pay? Unemployment, Negative Equity, and Strategic Default'' (with Kris Gerardi, Kyle Herkenhoff, and Lee Ohanian). 2018. \textit{Review of Financial Studies} 31(3): 1098--1131.
\item ``Payment Size, Negative Equity, and Mortgage Default'' (with Andreas Fuster). 2017. \textit{American Economic Journal: Economic Policy} 9(4): 167--91.
\item ``The Role of Proximity in Foreclosure Externalities: Evidence From Condominiums'' (with Lynn M. Fisher and Lauren Lambie-Hanson). 2015. \textit{American Economic Journal: Economic Policy} 7(1): 119--140.
\item ``Foreclosure Externalities: New Evidence'' (with Kristopher S. Gerardi, Eric Rosenblatt, and Vincent W. Yao). 2015. \textit{Journal of Urban Economics} 87: 42--56.
\item ``Mandated Risk Retention in Mortgage Securitization: An Economist's View.'' 2014. \textit{American Economic Review} 104(5): 82--87.
\item ``Identifying the Effect of Securitization on Foreclosure and Modification Rates Using Early-payment Defaults'' (with Manuel Adelino and Kris Gerardi). 2014. \textit{Journal of Real Estate Finance and Economics} 49(3): 352--378.
\item ``Why Don't Lenders Renegotiate More Home Mortgages? Redefaults, Self-Cures and Securitization'' (with Manuel Adelino and Kris Gerardi). 2013. \textit{Journal of Monetary Economics} 60(7): 835--853.
\item ``Do Borrower Rights Improve Borrower Outcomes? Evidence from the Foreclosure Process'' (with Kris Gerardi and Lauren Lambie-Hanson). 2013. \textit{Journal of Urban Economics} 73(1): 1--17.
\item ``How Effective Were the Federal Reserve Emergency Liquidity Facilities? Evidence from the AMLF'' (with Burcu Duygan-Bump, Patrick Parkinson, Eric Rosengren, and Gustavo A. Suarez). 2013. \textit{Journal of Finance} 68(2): 715--737.
\item ``Insuring Consumption Using Income-Linked Assets'' (with Andreas Fuster). 2011. \textit{Review of Finance} 15(4): 835--873.
\item ``The Impact of Deregulation and Financial Innovation on Consumers: The Case of the Mortgage Market'' (with Kristopher Gerardi and Harvey Rosen). 2010. \textit{Journal of Finance} 65(1): 333--360.
\item ``Reducing Foreclosures'' (with Chris Foote, Kris Gerardi, and Lorenz Goette). 2009. \textit{NBER Macroeconomics Annual} 24: 69--159.
\item ``Making Sense of the Subprime Crisis'' (with Kris Gerardi, Andreas Lehnert, and Shane Sherlund). 2008. \textit{Brookings Papers on Economic Activity} Fall: 69--145.
\item ``Just the Facts: An Initial Analysis of the Subprime Crisis'' (with Chris Foote, Kris Gerardi, and Lorenz Goette). 2008. \textit{Journal of Housing Economics} 17(4): 291--305.
\item ``Negative Equity and Foreclosure: Theory and Evidence'' (with Chris Foote and Kris Gerardi). 2008. \textit{Journal of Urban Economics} 64(2): 234--245.
\item ``Social Security and Unsecured Debt'' (with Erik Hurst). 2007. \textit{Journal of Public Economics} 91: 1273--1297.
\item ``Borrowing Costs and the Demand for Equity over the Life-cycle'' (with Steve Davis and Felix Kubler). 2006. \textit{Review of Economics and Statistics} 88(2): 348--362.
\item ``Educational Opportunity and Income Inequality'' (with Igal Hendel and Joel Shapiro). 2005. \textit{Journal of Public Economics} 89: 841--870.
\item ``New Financial Markets: Who Gains and Who Loses.'' 2005. \textit{Economic Theory} 26(1): 141--166.
\end{enumerate}

\section*{Other Publications}
\begin{enumerate}[leftmargin=*, nosep]
\item ``Lessons Learned from Housing Policy during COVID-19'' (with Kris Gerardi, Lauren Lambie-Hanson, Laurie Goodman, and Susan Wachter). 2022. In \textit{Recession Remedies}. Brookings Institution.
\item ``Mortgage-Default Research and the Recent Foreclosure Crisis'' (with Chris Foote). 2018. \textit{Annual Review of Financial Economics} 10: 59--100.
\item ``Evaluating Policies to Prevent Another Crisis: An Economist's View.'' 2014. \textit{Cato Papers on Public Policy} 3.
\item ``Occupation-level Income Shocks and Asset Returns'' (with Steve Davis). 2013. \textit{Quarterly Journal of Finance} 3(03n04).
\item ``The Rising Gap Between Primary and Secondary Mortgage Rates'' (with Andreas Fuster, Laurie Goodman, David Lucca, Laurel Madar, and Linsey Molloy). 2013. \textit{FRBNY Economic Policy Review}.
\item ``Why Did So Many People Make So Many Ex Post Bad Decisions? The Causes of the Foreclosure Crisis'' (with Kris Gerardi and Chris Foote). 2012. In \textit{Rethinking the Financial Crisis}. Blinder, Lo, and Solow, eds.
\item ``US Mortgage and Foreclosure Law'' (with Zachary Kimball). 2012. In \textit{The New Palgrave Dictionary of Economics}.
\item ``The Subprime Mortgage Crisis'' (with Chris Foote). 2011. In \textit{The New Palgrave Dictionary of Economics}.
\item ``Subprime Mortgages, Foreclosures, and Urban Neighborhoods'' (with Kristopher Gerardi). 2009. \textit{B.E. Journal of Economic Analysis \& Policy} 9(3): Article 12.
\item ``The Theory of Optimal Life-Cycle Saving and Investing'' (with Zvi Bodie and Jonathan Treussard). 2008. In \textit{Private Wealth}. CFA Institute/Wiley.
\item ``Income Shocks, Asset Returns, and Portfolio Choice'' (with Steve Davis). 2001. In \textit{Innovations in Retirement Financing}. University of Pennsylvania Press.
\end{enumerate}

\section*{Work in Progress}
\begin{itemize}[leftmargin=*, nosep]
\item ``Twisting ARMs: Who Won and Who Lost from the LIBOR to SOFR Cramdown'' (with Deborah Lucas and John R Wilson)
\item ``Prices vs. Quantities Revisited: What Do Policy-Makers Need to Know to Set Pigouvian Taxes and Subsidies?'' (with Denise DiPasquale, Edward Glaeser, and Adam M. Guren)
\item ``The Effect of Land Supply for New Homes on Residential Investment and House Prices'' (with Justin Katz)
\end{itemize}

\section*{Older Working Papers}
\begin{itemize}[leftmargin=*, nosep]
\item ``The Failure of Supervisory Stress Testing: Fannie Mae, Freddie Mac, and OFHEO'' (with Kris Gerardi and Scott Frame) -- R\&R, \textit{Review of Financial Studies}
\item ``Subprime Outcomes: Risky Mortgages, Homeownership Experiences, and Foreclosures'' (with Kris Gerardi and Adam Shapiro). Boston Fed Working Paper 07-15, 2007.
\item ``Collateralized Borrowing and Life-Cycle Portfolio Choice'' (with Felix Kubler). NBER Working Paper 12309, 2006.
\item ``Incomplete Markets and Trade.'' Boston Fed Working Paper 04-8, 2004.
\item ``On the Gains to International Trade in Risky Financial Assets'' (with Steve Davis and Jeremy Nalewaik). NBER Working Paper 7796, 2000.
\item ``Using Financial Assets to Hedge Labor Income Risks: Estimating the Benefits'' (with Steve Davis). 2000.
\end{itemize}

\section*{PhD Students Advised}
\begin{itemize}[leftmargin=*, nosep]
\item Eric Hardy, BU 2024 (Fannie Mae)
\item Lara Loewenstein, Brandeis 2018 (Cleveland Fed)
\item Jaclene Begley, NYU 2014 (Fannie Mae)
\item Lauren Lambie-Hanson, MIT 2013 (Philadelphia Fed)
\item Andreas Fuster, Harvard 2011 (EPF Lausanne)
\item Alex Kaufman, Harvard 2010 (Board of Governors)
\item Kristopher Gerardi, BU 2008 (Atlanta Fed)
\end{itemize}

\section*{Congressional Testimony}
\begin{itemize}[leftmargin=*, nosep]
\item U.S. Senate Committee on Banking, Housing, \& Urban Affairs -- ``Preserving Homeownership'' (July 2009)
\item U.S. House Committee on Financial Services -- ``Making Home Affordable Program'' (September 2009)
\item Congressional Oversight Panel, TARP -- Philadelphia Field Hearing (September 2009)
\item U.S. Senate Committee on Banking, Housing, \& Urban Affairs -- ``Housing Finance Reform'' (October 2011)
\item Massachusetts State Legislature -- Mortgage Refinancing Commission (July 2012)
\end{itemize}

\vfill
\begin{center}
\textit{Updated \today}
\end{center}

\end{document}
